Learning Causally-Generated Stationary Time Series

### 2017-02-24 doc/paper.tex
Added prior over kernels visualisation

\Cref{mod:cgpcm2} reveals the CGCPM as a Gaussian process in which the kernel, or equivalently the power spectral density (PSD), is modelled nonparametrically. \Cref{fig:interpolation} illustrates the generative process of the CGPCM: First, a filter $h$ is generated. Then, the kernel $k_{f\cond h}$ is constructed. Finally, a sample $f\cond h$ is drawn from $\mathcal{GP}(0,k_{f \cond h}(t-t'))$.

@@

@@

\section{Discussion}
We have presented the CGPCM as a model of causal, spectrally complex dynamical phenomena. Inference in the CGPCM is performed in a two-step procedure: first a collapsed varational MF approach is used to obtain an initial approximation, and then this approximation is refined through a variational SMF approach combined with ESS. The CGPCM has been tested and validated on synthesised and real-world signals and showed promising results. In particular, the CGPCM showed the capability of modelling rough signals without attributing this roughness to observation noise.

>>>>

\Cref{mod:cgpcm2} reveals the CGCPM as a Gaussian process in which the kernel, or equivalently the power spectral density (PSD), is modelled nonparametrically. \Cref{fig:interpolation} illustrates the generative process of the CGPCM: First, a filter $h$ is generated. Then, the kernel $k_{f\cond h}$ is constructed. Finally, a sample $f\cond h$ is drawn from $\mathcal{GP}(0,k_{f \cond h}(t-t'))$. \Cref{fig:prior} visualises the corresponding prior over kernels.

@@

 \begin{figure}[t]
    \centering
    \begin{tabularx}{\linewidth}{>{\centering}X>{\centering}X}
        GPCM & CGPCM
    \end{tabularx}
    \includegraphics[width=\linewidth, height=3cm]{resources/prior.pdf}
    \caption{Prior distribution over kernels in the GPCM and CGPCM}
    \label{fig:prior}
\end{figure}

@@

\section{Discussion}
We have presented the CGPCM as a model of causal, spectrally complex dynamical phenomena. Inference in the CGPCM is performed in a two-step procedure: first a collapsed varational MF approach is used to obtain an initial approximation, and then this approximation is refined through a variational SMF approach combined with ESS. The CGPCM has been tested and validated on synthesised and real-world signals and shows encouraging results. In particular, the CGPCM shows the capability of modelling rough signals without attributing this roughness to observation noise.
